%ACKNOWLEDGEMENTS page. 
%This page is optional

\clearpage
\begin{center}

\vspace*{5\baselineskip}
\textbf{\large Acknowledgements}
\end{center}

\begin{flushleft}
\hspace{10mm}I would first and foremost like to thank my advisor, Michael Tuts, for his support and guidance throughout the past few years. Mike, you have provided me with unwavering counsel through two international moves, the selection of this analysis topic, and the chaotic journey towards completing this thesis. I am very grateful for the creative direction I have been allowed to take this work in, making it truly my own.\\
\hspace{10mm}I would also like to thank John Parsons and Gustaaf Brooijmans for their mentorship during my time at Columbia. I have learned so much from both of you, through my work at Nevis Laboratories, through my coursework, and through the variety of Columbia ATLAS projects I have been fortunate to work on during my time at Columbia.\\
\hspace{10mm}These acknowledgements would be tragically incomplete without the mention of Julia Gonski, my colleague, former post-doc, and personal role model. Julia, I have learned so much from you about how to navigate scientific problem-solving, collaboration, and life in general. From the bottom of my heart, thank you for your heroic efforts and unwavering dedication to this project and to my success, even through your own career transition.\\
\hspace{10mm}I am very grateful to the many ATLAS students I have grown with and learned from during my time at Columbia. Andrew, Daniel, Gabriel, Kiryeong, Eleanor, Alan and Kiley, thank you so much for always answering my Skype messages, offering encouragement and wisdom, and to Gabe and Kiryeong in particular for your hard work on this analysis.\\
\hspace{10mm}To my friends and family who have helped me celebrate my victories and supported me in my times of need over the past 6 years, I could never have done this without you. Thank you Mom and Dad for believing in me every time I doubted myself, and encouraging me to pursue my passions. And to my fianc\'e Tayo - words cannot express how grateful I am for your steadfast support, whether you were 10 feet or 1,000 miles away. Thank you for always being there for me.\\
\hspace{10mm}Lastly, I would like to thank Huckleberry Roasters and Tonantzin Casa de Caf\'e, my two wonderful local coffee shops. Without your delicious caffeine, fast wifi, and distraction free work environment, I would never have managed to complete this thesis.
\end{flushleft}
\clearpage

%\pagenumbering{gobble}  %remove page number on summary page


