\chapter{Machine Learning Tools}
\label{ch:ml_tools}

\section{Introduction}
The search for semi-visible jets presents an opportunity to use novel machine learning (ML) tools to uncover patterns in the behavior of dark QCD. The subtlety of the shower differences between dark QCD (signal) and SM QCD (background) motivates a complex model that can accept high-dimensional low-level information, such as travel level information, to best understand key differences between signal and background correlations. Additionally, the large number of theory parameters which can be chosen arbitrarily and affect the shape of the dark QCD shower motivate exploring a data-driven machine learning approach, which could be sensitive to a wider variety of dark QCD behavior. \par

To this end, two machine learning approaches are developed for this search, which are used in tandem. The first is a supervised ML method where the ML algorithm is built to maximize exclusion sensitivity to the specific generated SVJ signal models used in this analysis. Here, supervised refers to the use of full and correct \textit{labels}\footnote{In machine learning a label refers to the correct identification information for an input. In the case of the binary classifier algorithm discussed here, the label is either ``signal" or ``background".} for all events considered during model training, which necessitates training over simulated data. The second is a semi-supervised method, where training of the model is data-driven and labels are only partially provided during training. The semi-supervised ML algorithm broadens the discovery sensitivity of the search, and reduces the dependence on the exact theory parameters chosen for signal model simulation. \par

The two different ML algorithms used in this approach will be explained in the following sections, along with their application in the SVJ analysis strategy.

\input{sections/pfn}
\input{sections/antelope}